Computing properties of independent sets by generic programming tensor networks \thanks{\funding{...}}

### 2021-09-23 paper/paper.tex

\begin{figure} 
    \centering
    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
    \caption{The statistics of Hamming distances between two MIS configurations for a specific three regular graph instance of size $200$.}
    \label{fig:hamming}
\end{figure}

>>>>

With the ability to enumerate configurations, we can analyse the landscape of the target problem, like the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
We compute all MIS configurations for two random 3 regular graph instances of size 200, and show the Hamming distance statistics in \Fig{fig:hamming}.
Some figure has single peak structure while some other has multiple peaks. Multiple peak structure indicates disconnected clusters in the configuration space.
\begin{figure} 
    \centering
    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
    \caption{The statistics of Hamming distances between two MIS configurations for two specific three regular graph instance of size $200$.}
    \label{fig:hamming}
\end{figure}
